ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
MOre edits

\author{Jacobus C. Lock\inst{1} \and
  Grzegorz Cielniak\inst{1} \and
  Andrea G. Tramontano\inst{2} \and
  Nicola Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universit\`{a} degli studi di Padova, Italy
}

@@

It is estimated that there are almost half a billion people today that live with mild to severe levels of vision impairments or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements ideas from the active vision field~\cite{bajcsy2017,bellotto2013}, but replaces the electro-mechanical servo typically found in active vision systems, with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

@@

Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
This work makes the following contributions:

@@

Section~\ref{sec:previous-work} discusses relevant work that has already been done, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively. 
The experiments that were conducted in this work, and their results, are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

@@

Making a mobile device that can detect objects and guide a PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing power and image processing methods.
Early attempts to solve this guidance problem made use of special markers encoded with object or environmental information, and a smartphone that can scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. 
The device uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send the desired object and a photo of their environment to a Mechanical Turk worker or volunteer that sends the position of the requested object within the picture back to the user.

The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment, which is remedied by markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance is provided. 
The systems in~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is significant lag, and a reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out of view object and proved that this is a viable method to search for an object. 
However, this work relied on physical barcodes encoded with object information to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

Object detectors can be divided into two main categories: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates. 
In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and implement a POMDP that can handle observation uncertainties in object detectors and classifiers.

@@

The POMDP module that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads tot he target object.
The waypoint positions are based on the model's pre-trained internal knowledge on the inter-object spatial relationships and they are placed in a way that maximises the probability of the user pointing to and finding the target object.
A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.

@@

A POMDP model is represented by the $8$-tuple

\begin{equation*}
  (\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma),
\end{equation*}

\noindent where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate. 
$\mathbf{b}$ is updated for every timestep and action-observation pair.
Each of the POMDP's parameters are discussed next. 
%This update is done with

@@

The reward function is designed to encourage the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action it takes that does not results in it finding the target object.
Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) and when it exceeds some search length threshold denoted by $n_{\max}$.
The rewards are summarised in Table~\ref{tab:rewards}.

\begin{table}[h]
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{1cm}}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \textrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

The observations the controller can make are identical to the states that the mobile device can enter. 
In this case, however, uncertainty is introduced to the observation by the object detector.
Previous search locations and search time is perfectly observable in this case, since these can be tracked by the mobile device.
$\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
These values were found by performing a set of classifier tests on the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.

@@

We encoded a total of 16 objects, including a `nothing' state where the detector does not see anything of interest, into the controller and object detector.
These objects are given by $\mathbf{U}$, defined as

@@

We also set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.

The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.

\todo{maybe remove references here}
The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,kaelbling1998planning,silver2010monte,spaan2005perseus} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\cite{aitoolbox} to solve the POMDP model.
The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

ActiVis's target audience are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to ambient sounds (something PwVI typically rely upon), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle. 
A similar interface was used in~\cite{schauerte2012assistive}.
With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.

@@

The SSD-Lite network is a single-stage object detection and classification network that is based on the SSD architecture that uses MobileNetV2~\cite{sandler2018mobilenetv2} for its backbone.
This is a lightweight model that has less parameters and requires relatively little memory to perform inference tasks, which makes it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
The full SSD model on the other hand achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
Tiny-DSOD~\cite{li2018tinydsod} is a mobile alternative to SSD-Lite with similar accuracy and computing requirements(mAPs$=0.23$, parameters$=$1.15M, FLOPS$=$1.12B).
However, we found that the SSD-Lite version produced better results in this application and we chose to implement it into our system.

The network was trained with a maximum of 10000 annotated object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{A}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android. 
%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
%\todo{add mAPs we achived}

@@

When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} and moves the device into a new grid square or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses the new $\omega$ to update $\mathbf{b}$ queries the policy for the best location to place the new waypoint. 
The policy output is an action from the action set $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint.
For example, an `UP' output would result in the waypoint being placed one grid square above the current grid square within view.

>>>>

\author{J.C. Lock\inst{1} \and
  G. Cielniak\inst{1} \and
  A.G. Tramontano\inst{2} \and
  N. Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universit\`{a} degli studi di Padova, Italy
}

@@

There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
The work we present here is part of the ActiVis project that aims to assist people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

@@

ActiVis uses the camera's current and previous image data as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to take to reach the target object.
To enable this, we expanded upon our previous work and implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone that generates real-time navigation instructions to guide the user to their target object.
This work makes the following contributions:

@@

Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively. 
The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

@@

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses a feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz} requires the user to send a photo of their environment to a Mechanical Turk worker that sends the position of the requested object within the picture back to the user.

The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
The system in~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to help guide a user to the correct location, but the there is significant lag and a reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out-of-view object and proved that this is a viable method to search for an object. 
However, this work used barcodes encoded with object information to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector's classification errors that influence the action that \emph{K} generates. 
In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and implement a POMDP that can handle classification uncertainties in object detectors and classifiers.

@@

The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.

@@

A POMDP model is represented by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate. 
%$\mathbf{b}$ is updated for every timestep and action-observation pair.
Each of the POMDP's parameters are discussed next. 
%This update is done with

@@

The reward function encourages the device controller to search for and find the target object by giving it a substantial reward for doing so, while penalising it for every action that does not result in it finding the target object.
Furthermore, additional penalties are given if the controller generates a waypoint in an area it has explored before $(v = \textrm{true}$) or when it exceeds some search length threshold denoted by $n_{\max}$.
The rewards are summarised in Table~\ref{tab:rewards}.

\begin{table}
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{1cm}}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \textrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

The state observations are identical to the states that the mobile device can enter. 
In this case, however, uncertainty is introduced into the observation by the object detector.
Previous search locations and search time are fully observable here, since they can be tracked by the mobile device.
$\mathbf{\Omega}$ therefore only contains the classification/misclassification probabilities of the object detector. 
These values were found by performing a set of classifier tests on the object detector and generating a confusion matrix to populate $\mathbf{\Omega}$.

@@

We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector.
These objects are defined as

@@

\noindent We set $n_{\max}$ to 12 waypoints, after which the agent gets penalised for every additional waypoint it generates that does not lead to the target object. 
This results in a total of 352 reachable states ($n_{states} = 16\times11\times2$), with any state containing the target object acting as a terminal state.

The POMDP model is put through a training process to generate a policy that contains the optimal belief-action mapping that the controller can use to produce the optimal waypoint locations.
This is done by having the model explore the entire state-action-observation space and optimising the policy to maximise its long-term cumulative reward.
The difficulty of solving POMDPs is that $\mathbf{b}$ is a vector of continuous probability distributions with infinite combinations, making POMDPs time-consuming or even impossible to solve exactly.
We found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
Multiple algorithms have been proposed~\cite{bargiacchi2016dynamic,silver2010monte} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} as implemented in the AI-Toolbox library~\footnote{github.com/Svalorzen/AI-Toolbox} to solve the POMDP model.
The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking these points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to ambient sounds, we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly. 
A similar approach was used in~\cite{schauerte2012assistive}.
With this interface and headset, ActiVis is able to describe location of a waypoint to a user in the pan and tilt dimensions.

@@

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

The network was trained with a maximum of 10000 object samples, taken from the OpenImages dataset~\cite{openimages}, for each object class in $\mathbf{U}$ with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAPs of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android. 
%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
%\todo{add mAPs we achived}

@@

When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.
